Throughput Prediction on 60 GHz Devices for Latency Sensitive Applications

### 2021-01-21 paper.tex
changes

To understand how the model performs for each trace, we picked the best model for each trace at each timescale, and calculated the RMSE. The results are shown in Figure \ref{figure: RMSE for Static Traces}.

@@

We start with all $N$ features. For each of the feature, we temporarily remove it from the input, and train a model using the remaining $N-1$ features. This procedure identifies the least useful feature among $N$ features, and we permanently remove this feature from the input. Then, we iterative perform the same procedure on the rest $N-1$ features, until all features have been removed. Effectively, this algorithm ranks the features by usefulness. The result of our experiments is shown in Table \ref{tab: Static Feature Selection}.

>>>>

To understand how the model performs for each trace, we picked the best model for each trace at each timescale, and calculated the RMSE. The results are shown in Figure~\ref{figure: RMSE for Static Traces}. \comment{We observe that ???}

@@

We start with all $N$ features. For each of the features, we
temporarily remove it from the input, and train a model using the
remaining $N-1$ features. We then compare the resulting models
and identify the least useful
feature among $N$ features as the one after removing which results in the model
with the least prediction accuracy reduction. We permanently remove this feature
from the input, and then iteratively repeat the procedure on the
remaining $N-1$ features, until all features have been
removed. Effectively, this algorithm ranks the features by
usefulness. The result of our experiments is shown in Table \ref{tab:
  Static Feature Selection}.
